---
title: "QC report - Untargeted lipidomics"
author: "R.J.E. Derks"
date: "`r Sys.Date()`"
output: 
  html_document:
    toc: true
    toc_float: true
params:
  analysis_data: NA
  trend_data: NA
  rsd_data_overall: NA
  rsd_data_batch: NA
  selected_pools: NA
  selected_samples: NA
  rsd_cutoff: NA
---

```{r setup, include=FALSE}
# do not add any code
knitr::opts_chunk$set(echo = FALSE)

library(lipidomics2)
library(sessioninfo)
library(ggplot2)
library(plotly)

# get all the information/data
analysis_data <- params$analysis_data
trend_data <- params$trend_data
qc_data <- params$qc_data
rsd_data_overall <- params$rsd_data_overall
rsd_data_batch <- params$rsd_data_batch
selected_pools <- params$selected_pools
selected_samples <- params$selected_samples
rsd_cutoff <- params$rsd_cutoff
```

# Introduction

This report gives an overview of the Quality Control samples measured.

# QC

## Overall RSD {.tabset}

Overall overview RSD values. Lipids above the threshold of **`r rsd_cutoff`** are excluded.

### Overall

```{r fig.width=10}
show_overall_hist(data = rsd_data_overall,
                  rsd_cutoff = rsd_cutoff)
```

### Batch

```{r fig.width=10}
show_batch_hist(data = rsd_data_batch,
                rsd_cutoff = rsd_cutoff)
```

## RSD per lipid class {.tabset}

RSD values per lipid class.

### Overall

```{r fig.width=10, fig.height=7, warning=FALSE, message=FALSE}
show_class_overall_violin(data = rsd_data_overall,
                          rsd = rsd_cutoff)
```

### Batch

```{r fig.width=10, fig.height=7, warning=FALSE, message=FALSE}
show_class_batch_violin(data = rsd_data_batch,
                        rsd = rsd_cutoff)
```

## Trend plot {.tabset}

### Overall

```{r fig.width=10, fig.height=7}
trend_plot(trend_data = trend_data,
           type = "overall")
```

### Per batch

```{r fig.width=10, fig.height=7}
trend_plot(trend_data = trend_data,
           type = "batch")
```

## Correlation

Quick comparison between the samples.

```{r include=FALSE}
fig_height_cor_heatmap <- ceiling(length(unique(analysis_data$sample_name)) / 7)
if(fig_height_cor_heatmap < 6) {
  fig_height_cor_heatmap <- 6
}
```

```{r fig.width=10, fig.height=fig_height_cor_heatmap}
cor_df <- calc_cor(data = analysis_data,
                   idx_pools = selected_pools,
                   idx_samples = selected_samples)

p <- qc_cor_plot(data = cor_df)

ply <- plotly::ggplotly(p = p)
ply
```

# Session info

```{r session_info}
session_info()
```

